\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4in,top=0.4in,right=0.4in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Amit Kumar Jha} % Your name
% You can merge both of these into a single line, if you do not have a website. 
\address{\href{mailto:amitkumarjha71@gmail.com}{amitkumarjha71@gmail.com} \\ \href{https://www.linkedin.com/in/amitkumarjha1996/}{linkedin.com/in/amitkumarjha1996/} \\ +91-9740473139, +91-9986041196}  %

\begin{document}

%----------------------------------------------------------------------------------------
% OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Objective}
To work in an organization with a professional work-driven environment where I can utilize my potential and enhance my knowledge and skills to contribute to society in the IT Sector \& its management field along with the achievement of an organizational goal, willing to establish myself as a versatile Engineer.

As an ambitious professional seeking full-time opportunities in Linux/UNIX Admin, Middleware Admin, WebLogic Admin \& DevOps, I am eager to expand my expertise, learn new skills, and contribute effectively to any team. With a strong work ethic and a dedication to continuous learning, I am open to exploring various roles and industries that align with my skills and interests. I am committed to delivering outstanding results and making a meaningful impact wherever I go.
\end{rSection}

%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Dr. M.G.R. Educational and Research Institute}, Chennai, Tamil Nadu, India \hfill {Sep 2019}
\\ Bachelor of Technology (B.Tech.) in Computer Science and Engineering (CSE) \hfill \textit{CGPA: 7.78}

{\bf Dr. J.N Mishra College}, BSEB Board \hfill {May 2015}
\\ Graduated, Division 1st \hfill \textit{Marks: 61\%}

{\bf RSM Public School}, CBSE Board \hfill {May 2012}
\\ Graduated \hfill \textit{CGPA: 7.2}
\end{rSection}

%----------------------------------------------------------------------------------------
% PROFESSIONAL CERTIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Professional Certifications}
\begin{itemize}
    \item Microsoft Certified: DP-900: Azure Data Fundamentals
    \item Microsoft Certified: AZ-204: Azure Developer Associate
    \item Microsoft Certified: AZ-900: Azure Fundamentals
    \item Microsoft Certified: AZ-104: Azure Administrator Associate
    \item Microsoft Certified: AZ-400: DevOps Engineer Expert
    \item Academy Accreditation - Generative AI Fundamentals
    \item AWS Security Fundamentals
    \item Official (ISC)² Certified in Cybersecurity (CC)
    \item RPA Developer Foundation
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
% WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\textbf{Software Engineer} \hfill May 2022 - Present\\
\textbf{Tech Mahindra}, Bengaluru, India
\begin{itemize}
    \item Project \#1: AT \& T
    \item Installing, configuring, maintaining, upgrading, and providing support for application environments.
    \item Supporting multiple WebLogic Oracle 12c, IIS, Apache Tomcat, and MQ servers.
    \item Deploying web-based apps, J2EE application archives (JAR, WAR, EAR, RAR), and Batch files.
    \item SSL certificate installation on WebLogic and Apache web servers.
    \item Upgrading and patching WebLogic and middleware components.
    \item Debugging and resolving issues related to application configuration and technology.
    \item Disaster recovery failover testing and business continuity strategies.
    \item Creating and maintaining automation scripts.
    \item Publishing and maintaining internal documentation.
    \item Infrastructure support for Oracle utilities and security patch application.
    \item Linux operational tasks and coordinating with L2/L3 team members.
    \item Weekly or monthly OS patching and deployment for system security and stability.
    \item Project \#2: DiGi Malaysia
    \item Lead Unix system administration, scripting, and security efforts.
    \item Technical guidance, automation scripts development, and compliance with security standards.
    \item Facilitating knowledge sharing and enhancing system performance, reliability, and security.
\end{itemize}

\textbf{Senior Technical Engineer} \hfill Nov 2021 - Apr 2022\\
\textbf{Quess Corp Limited}, Bengaluru, India
\begin{itemize}
    \item Project \#1: Huawei
    \item Data Migration: Migration of Huawei data from third-party systems.
    \item OCS/CBS Products: Worked with Huawei OCS/CBS products.
    \item Product Catalog and Tariff Configuration.
    \item NGBSS and BES Modules.
\end{itemize}

\textbf{DevOps Engineer} \hfill Jul 2020 - Oct 2021\\
\textbf{OnMobile Global Limited}, Bengaluru, India
\begin{itemize}
    \item Issue Identification and Resolution.
    \item Software Scalability.
    \item Version Control System.
    \item User Feedback Monitoring.
    \item Environment Setup Design.
    \item Incident Management.
    \item Technology Support.
    \item Telecom Service Provisioning.
    \item Platform Restarts.
    \item NOVA Reports Generation.
    \item Automatic Jobs and Cron Jobs.
    \item Disk Space Management.
    \item Networking Operations.
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
% INTERNSHIP & TRAINING SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Internship \& Training}

\textbf{Telecom Intern} \hfill {BSNL, Saharsa, Bihar, India}
\begin{itemize}
    \item Signaling Concepts.
    \item Digital Transmission Systems.
    \item Mobile Technologies (2G to 5G).
    \item Broadband Technologies.
    \item Industry Trends.
    \item Certification: Received certification from BSNL-Saharsa.
\end{itemize}

\textbf{Web Dev Intern} \hfill {Bals Technology, Chennai, Tamil Nadu, India}
\begin{itemize}
    \item C\# Language.
    \item Relational Database Model.
    \item Database Management.
    \item Web Development with Asp.Net.
\end{itemize}

\textbf{Network Intern} \hfill {Sans Bound Solutions Pvt Ltd, Chennai, Tamil Nadu, India}
\begin{itemize}
    \item Network Performance Enhancement.
    \item Network Equipment Configuration.
    \item Infrastructure Management.
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
% PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\textbf{Online Newspaper Application (OLNP)}
\begin{itemize}
    \item Objective: Develop an Android-based application for sharing daily college-related news.
    \item Abstract: Design and develop a dynamic mobile application for college students.
    \item Functionalities: Users can see headlines, thumbnail images, detailed write-ups, images, audio, videos, and referral links.
    \item Languages Used: C++, Java, HTML \& CSS.
    \item Project URL: \href{https://apkfab.com/androidtestui/com.mgr.cse.olnp/apk}{https://apkfab.com/androidtestui/com.mgr.cse.olnp/apk}
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
% SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills & Linux/Unix Administration, Middleware Administration, WebLogic Administration, DevOps, Cloud Computing (AWS, GCP, Azure), Oracle Applications (E-Business Suite, PeopleSoft, WebLogic), Telecom Networks (BSS, OSS, RBT, CBS, TCP/IP, LAN, WAN, DNS, DHCP) \\
Programming & JavaScript, HTML, CSS, Bash Scripting, Shell Scripting, Python \\
Tools/Technologies & Apache, Nginx, WebLogic, WebSphere, Glassfish, JBoss, Apache Tomcat, Super PuTTY, WinSCP, VNC, TAPm, Thruk, Wireshark, Soap UI, Jira, ServiceNow \\
Operating Systems & CentOS, Ubuntu, Windows, macOS \\
Databases & SQLite3, MySQL, PostgreSQL, Oracle DB, IBM DB2 \\
Applications & Word, PowerPoint, Excel, Google Collab, Power BI \\
\end{tabular}
\end{rSection}

%----------------------------------------------------------------------------------------
% AREA OF INTEREST SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Area of Interest}

\begin{itemize}
    \item System Administration (Linux/Unix)
    \item Middleware Administration (WebLogic, WebSphere)
    \item Telecommunications (BSS, OSS, Network Protocols, RBT, OCS, CBS)
\end{itemize}
\end{rSection}

\end{document}
